\LARGE \bf Human-Robot Interaction: A Deliberative Architecture

### 2013-07-24 paper.tex
Reinforce the AI orientation of the introduction

This paper addresses some key decisional issues that are necessary for a
cognitive robot which shares space and tasks with a human. We adopt a
constructive approach based on the identification and the effective
implementation of individual and collaborative skills. The system is
comprehensive since it aims at dealing with a complete set of abilities
articulated so that the robot controller is effectively able to conduct in a
flexible manner a collaborative task with a human partner. These abilities
include geometric reasoning and situation assessment based essentially on
perspective-taking and affordances, management and exploitation of each agent
(human and robot) knowledge in a separate cognitive model, human-aware task
planning and human and robot interleaved plan achievement.

@@

\begin{keyword}
    %% keywords here, in the form: keyword \sep keyword

    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)

@@

Human-robot interaction requires to equip the robot with explicit
reasoning on the human and on its own capacities to achieve its tasks
in a collaborative way with a human partner. This paper presents a
robot control system which has been especially designed for a
cognitive robot which shares space and task with a human. We have
adopted a constructive approach based on effective individual and
collaborative skills. The system is comprehensive since it aims at
dealing with a complete set of abilities articulated so that the robot
controller is effectively able to conduct in a flexible manner a
collaborative task with a human partner.

We illustrate below how we deal with a typical human-robot interactive
task achievement and what are the abilities we claim are
necessary. Section \S\ref{sec:problem} proposes a typical human-robot
interaction problem that can be solved by the proposed robot
controller. Section \S\ref{sec:soa} reviews related work and analyses
the context of our contribution.  Section \S\ref{sec:Framework}
provides an overview of the robot controller and introduces three
activities which are described in \S\ref{sec:situ}, \S\ref{sec:plan}
and \S\ref{sec:action}. Finally, Section \S\ref{sec:expes} presents an
effective run on a real robot in face to face interaction with a
person.

@@

\begin{figure}[ht!]
   \label{fig:sparkSubfigures}
   \begin{center}
%
       \subfigure[Initial state]{%
%           \label{fig:wuweiPhoto}
           \includegraphics[width=0.5\textwidth]{./figs/etat2-P1010769_brightened-v2.jpg}
       }%
       \subfigure[3d model view of initial state]{%
%          \label{fig:sparkScreenshot}
          \includegraphics[width=0.43\textwidth]{./figs/etat2_photo.png}
       }\\ %  ------- End of the first row ----------------------%
%
   \end{center}

@@

\end{figure}

>>>>

This paper addresses some key decisional issues that are necessary for a
cognitive robot which shares space and tasks with a human. We adopt a
constructive approach based on the identification and the effective
implementation of individual and collaborative skills. The system is
comprehensive since it aims at dealing with a complete set of abilities
articulated so that the robot controller is effectively able to conduct in a
flexible manner a collaborative task with a human partner. These abilities
include geometric reasoning and situation assessment based essentially on
perspective-taking and affordances, management and exploitation of each agent
(human and robot) knowledge in separate cognitive models, human-aware task
planning, and human and robot interleaved plan achievement.

@@

\begin{keyword}
    %% keywords here, in the form: keyword \sep keyword
    human-robot interaction \sep cognitive robotics \sep perspective taking \sep knowledge representation and reasoning
    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)

@@

Human-robot interaction is a challenge for artificial intelligence. This field
indeed lays at the crossroad of several other domains of AI and requires to
tackle them in a holistic manner. Modeling humans and human cognition;
acquiring, representing, manipulating in a tractable way abstract knowledge;
reasoning on this knowledge to make decisions; instanciating those decisions
into physical actions in coordination with humans... Many AI techniques are
invited, from visual processing to symbolic reasoning, from task planing to
\emph{theory of mind} building, from reactive control to action recognition and
learning.

We do not tackle all these issues. This article attempts however to organize
them into a coherent challenge for artifical intelligence, and also explicit
some of the trails that have been explored on our robots and that result in a
deliberative, knowledge-focused, architecture for human-robot interaction.

Human-robot interaction requires to equip the robot with explicit reasoning on
the human and on its own capacities to achieve its tasks in a legible, if not
collaborative, way with human partners. In the following pages, we present a
robot control system which has been especially designed for a cognitive robot
which shares space and task with a human. It has been designed by adopting a
constructive approach based on effective individual and collaborative skills.
The system is comprehensive since it aims\fxnote{it *is* comprehensive, or it *aims* at being comprehensive?} at dealing with a complete set of
abilities articulated so that the robot controller is effectively able to
conduct in a flexible manner a collaborative task with a human partner.

We illustrate below how we deal with a typical human-robot interactive task
achievement and what are the abilities we claim are necessary. Section
\ref{sec:problem} proposes a typical human-robot interaction problem that can
be solved by the proposed robot controller. Section
\ref{sec:Framework} provides an overview of the robot controller and
introduces three activities which are described in \ref{sec:situ},
\ref{sec:plan} and \ref{sec:action}. Section \ref{sec:expes}
presents the structure an actual run on a real robot in face to face interaction with a
person. Finally, section~\ref{sec:soa} discusses and analyses the impact of
each of our contribution in the light of existing literature and alternative
approaches.

@@

\begin{figure*}[ht!]
   \label{fig:sparkSubfigures}
   \begin{center}
%
       \subfigure[Initial state]{%
%           \label{fig:wuweiPhoto}
           \includegraphics[width=0.5\textwidth]{./figs/etat2-P1010769_brightened-v2.jpg}
       }%
       \subfigure[3d model view of initial state]{%
%          \label{fig:sparkScreenshot}
          \includegraphics[width=0.43\textwidth]{./figs/etat2_photo.png}
       }\\ %  ------- End of the first row ----------------------%
%
   \end{center}

@@

\end{figure*}
